\chapter*{\centering{\large{ABSTRACT}}}

\begin{spacing}{1}
	\textbf{ALDIAN ASMARA}. \emph{Deisgning User Interface of a Search Engine with Admin Console for Managing and Visualizing Search Engine Indexing Result}. \emph{Thesis}. \emph{Faculty of Mathematics and Natural Sciences}, \emph{State University of Jakarta}. 2023. \emph{Supervised by} Muhammad Eka Suryana, M.Kom \emph{and} Med Irzal, M.Kom.
	\newline
	\newline
	\textit{The search engine is a computer program designed to assist users in finding information with specific keywords. In the research conducted by \citep{lazu}, an architecture for a search engine has been developed by integrating a web crawler, page ranking algorithm, and document ranking. The research has some shortcomings, such as the absence of an admin console for managing and visualizing of search engine's indexed data. The objective of this study is to provide a way for users to access the search engine along with an admin console for managing and visualizing the indexed data. Supporting information for this research is derived from literature studies of relevant journals and discussions held by researchers with stakeholders. The development process employed in this research follows the Scrum methodology, utilizing Python and Javascript technologies. The final result of this study is a user interface for the search engine admin panel to manage and visualize the indexed data in the created search engine. }
	\newline
	\newline
	\noindent \textbf{Keywords}: \textit{search engine}, \textit{application}, \textit{admin console}, \textit{scrum}
\end{spacing}

